1-generate-toys

### 2018-07-05 scripts/3-metric_characterisation/1old-generate_toys.Rmd
rename all mentions of dynalysis to dynbenchmark
dataset -> task

```{r setup}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(dynalysis)
library(tidyverse)
library(dyneval)
```

@@

toys$gs_grouped <- parallel::mclapply(toys$gs, group_task, mc.cores=8)

>>>>

```{r setup}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(dynbenchmark)
library(tidyverse)
library(dyneval)
```

@@

toys$gs_grouped <- parallel::mclapply(toys$gs, group_dataset, mc.cores=8)
